### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{figure}
  \begin{minipage}{0.48\linewidth}
    \resizebox{\linewidth}{!}{

@@

        \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
        \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;
        \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
      \end{tikzpicture}
    }
    \caption*{(a) Noiseless Lossless}
  \end{minipage}
  \hfill
  \begin{minipage}{0.48\linewidth}
    \resizebox{\linewidth}{!}{

@@

\begin{mydef}
  \label{def}
  Suppose we have a program $\beta$ with the input set $K$. We randomly select $k_1, k_2, \dots, k_n \in K' \subseteq K$ as the input. We denote it as
  $$\beta(K') \rightarrow	O'$$

@@

With Definition~\ref{def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively. In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed. Therefore, the information leakage is $log_2{8} = 3$ bits. In Figure~\ref{fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed. Therefore, the information leakage is $log_2{4} = 2$ bits. We test the program with $8$ inputs. Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$, according to Equation~\ref{eq1}. Therefore, the leakage in Figure~\ref{fig:example1} show the leakage is leaked totally.

\subsection{A Conservative Estimation}
In this section, we prove Definition~\ref{def} is the conservative estimation of the amount of leaked information based on the channel capacity.

>>>>

\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \resizebox{\linewidth}{!}{

@@

        \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
        \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;
        \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
        \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
      \end{tikzpicture}
    }
    \caption*{(a) Noiseless Lossless}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \resizebox{\linewidth}{!}{

@@

\begin{mydef}
  \label{chapter5:def}
  Suppose we have a program $\beta$ with the input set $K$. We randomly select $k_1, k_2, \dots, k_n \in K' \subseteq K$ as the input. We denote it as
  $$\beta(K') \rightarrow	O'$$

@@

With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively. In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed. Therefore, the information leakage is $log_2{8} = 3$ bits. In Figure~\ref{fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed. Therefore, the information leakage is $log_2{4} = 2$ bits. We test the program with $8$ inputs. Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$. According to Equation~\ref{chapter5:eq1}. the secret-dependent data accesses in Figure~\ref{fig:example1} can leak the sensitive information totally.

\subsection{A Conservative Estimation}
In this section, we prove Definition~\ref{chapter5:def} is the conservative estimation of the amount of leaked information based on the channel capacity.
